Incremental tactics

### 2012-05-07 doc/papers/LFMTP2012/paper.tex
paper

Note that this notion of substitution differs from hereditary
substitution found in \eg\ \cite{hl07mechanizing} as it presupposes
$\eta$-long normal forms: a non-empty spine cut against to another
non-empty spine $\gcut {\app H S} {S'}$ blocks the substitution
instead of reducing to $\app H {(\gconcat S S')}$ (an implicit
$\eta$-expansion). For example, the reduction $\gcut {\lam x \app
  {\var x}{\var x}} {\lam x \app {\var x}{\var x}}$ gets stuck because
the second $\var x$ in the left part is substituted by a function yet
is not itself a function.

@@

  \fbox{$\jm\mr\Gamma M A \mmr {M'}$}
  \qquad
  Object typing

@@

    % App
    \infer{
      \jf\mr\Gamma F \mmr {M'} {A'}
       \and
      \jea\mmr\Gamma A {A'}
    }{
      \jm\mr\Gamma F A \mmr {M'}
    }

@@

  \fbox{$\js\mr\Gamma\sigma{\Gamma'}\mmr{\sigma'}$}
  \qquad
  {Substitution typing}

@@

  \fbox{$\jf\mr\Gamma F \mmr M A$}
  \qquad
  {Application typing}

@@

  \fbox{$\jh\mr\Gamma H A L$}
  \qquad
  {Head typing}

@@

  \fbox{$\jl\mr\Gamma A S \mmr{S'}{A'}$}
  \qquad
  {Spine typing}

@@

Definitional equality judgement between two families $\jea\mr\Gamma A
{A'}$ is used by these typing rules. This equivalence is usually
defined to be just $\alpha$-equivalence since objects are in
$\beta\eta$-canonical form. Here, objects can contain metavariables
defined in $\mr$, so we shall thread it. Moreover, we will see in the
next section how defined constants compute and thus influence
definitional equality. Definitional equality is defined later in
\ref{fig:def-eq}.

@@

    \infer{
      \Sigma(a) = K
      % TODO
    }{
      \jfam\mr\Gamma {\app{\cst a} S} \mmr {\app{\cst a} {S'}}
    }

@@

>>>>

Note that this notion of substitution differs from hereditary
substitution found in \eg\ \cite{hl07mechanizing} as it presupposes
$\eta$-long normal forms: once a cut starts, there must be exactly as
many formal and actual arguments. A non-empty spine cut against
another non-empty spine $\gcut {\app H S} {S'}$ blocks the
substitution instead of reducing to $\app H {(\gconcat S S')}$ (an
implicit $\eta$-expansion); conversely, exhausting actual but not
formal arguments as in $\gcut{\lam x M}{\gnil}$ blocks the
substitution too. For example, the reduction $\gcut {\lam x \app {\var
    x}{\var x}} {\lam x \app {\var x}{\var x}}$ gets stuck because the
second $\var x$ in the left part is substituted by a function yet is
not itself a function.

@@

  \fbox{$\jm\mr\Gamma M A \mmr {M'}$}
  \qquad
  Object

@@

    % App
    \infer{
      \jf\mr\Gamma F \mmr {M'} {A'}
       \and
      \jea\mmr\Gamma {\app{\cst a} S} {A'}
    }{
      \jm\mr\Gamma F {\app{\cst a} S} \mmr {M'}
    }
    % TODO commenter type ground

@@

  \fbox{$\js\mr\Gamma\sigma{\Gamma'}\mmr{\sigma'}$}
  \qquad
  {Substitution}

@@

  \fbox{$\jf\mr\Gamma F \mmr M A$}
  \qquad
  {Application}

@@

  \fbox{$\jh\mr\Gamma H A L$}
  \qquad
  {Head}

@@

  \fbox{$\jl\mr\Gamma A S \mmr{S'}{A'}$}
  \qquad
  {Spine}

  \begin{mathpar}
    \infer{
      \jm\mr\Gamma M A \mmr {M'}
      \and
      \jl\mmr\Gamma {\gsubst{A'}{M'}} S \mmmr {S'} {A''}
    }{
      \jl\mr\Gamma {\prd x {A} {A'}} {\spinecons M S} \mmmr {\spinecons
      {M'}{S'}} {A''}
    }

    \infer{ }{
      \jl\mr\Gamma {\app{\cst a} S} \spinenil \mr \spinenil {{\app{\cst a} S}}
    }
  \end{mathpar}

@@

Definitional equality judgement between two families $\jea\mr\Gamma A
{A'}$ is used by these typing rules. This equivalence is usually
defined to be just $\alpha$-equivalence since objects are in
$\beta\eta$-canonical form. Here, objects can contain metavariables
defined in $\mr$, so we shall thread it. Moreover, we will see in the
next section how defined constants compute and thus influence
definitional equality. Definitional equality is defined later in Fig.
\ref{fig:def-eq}.

@@

    \infer{
      \Sigma(a) = K
      \and
      \jfl\mr\Gamma K S \mmr {S'}
      % TODO
    }{
      \jfam\mr\Gamma {\app{\cst a} S} \mmr {\app{\cst a} {S'}}
    }
  \end{mathpar}

  \fbox{$\jfl\mr\Gamma K S \mmr {S'}$}
  \qquad
  {Family spine}

  \begin{mathpar}
    \infer{
      \jm\mr\Gamma M A \mmr {M'}
      \and
      \jfl\mmr\Gamma {\gsubst{K}{M'}} S \mmmr {S'}
    }{
      \jfl\mr\Gamma {\prd x {A} {K}} {\spinecons M S} \mmmr {\spinecons
      {M'}{S'}}
    }

    \infer{ }{
      \jfl\mr\Gamma\type\spinenil\mr\spinenil
    }
  \end{mathpar}

@@

  \begin{mathpar}
    \infer{
      \jfam\mr\Gamma A\mmr{A'}
      \and
      \jkind\mmr{\envcons\Gamma x A} K \mmmr {K'}
    }{
      \jkind\mr\Gamma{\prd x A K}\mmmr{\prd x {A'}{K'}}
    }

    \infer{ }{\jkind\mr\Gamma\type\mr\type}
  \end{mathpar}
